\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
    linkcolor = red,
    urlcolor  = blue,
    citecolor = blue,
    anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\newfontfamily{\SansTC}[
    Path = Fonts/NotoSansTC/,
    Extension = .otf,
    BoldFont = NotoSansCJKtc-Bold.otf,
]{NotoSansCJKtc-Regular.otf}

\newfontfamily{\SerifTC}[
    Path = Fonts/NotoSerifTC/,
    Extension = .otf,
    BoldFont = NotoSerifTC-Bold.otf,
]{NotoSerifTC-Regular.otf}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\classesList}[4]{
    \item\small{
            {#1 #2 #3 #4 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

\begin{center}
{\Huge Yu-Wei Tseng} \\ \vspace{1pt}
\small
\faHouseUser\ No. 669 Zhongzheng West Road, Zhubei City, Hsinchu County, Taiwan R.O.C. \\ \vspace{1pt}
\raisebox{-0.1\height}\faPhone\ +886-972-913-737 ~
\href{mailto:dadavidtseng@gmail.com}{\faEnvelope\ dadavidtseng@gmail.com} ~
\href{https://linkedin.com/in/dadavidtseng}{\faLinkedin\ dadavidtseng}  ~
\href{https://github.com/dadavidtseng}{\faGithub\ dadavidtseng}
\vspace{-8pt}
\end{center}

% adjust vscape based on the space you want to leave between each section.




%-----------EXPERIENCE-----------
\section{Experiences}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://www.ctrls1890.com/}{CtrlS Ltd.}}{Nov 2023 -- Present}{Junior Game Programmer}{Tainan, Taiwan}
\resumeItemListStart
\resumeItem {Crafting applications with Unity Engine}
\resumeItem {Enabling the perusal of 360-degree AR streaming videos on mobile devices.}
\resumeItem {Leveraging UniRx facilitates the seamless handling of asynchronous operations and events.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.tap-arch.tw//en}
{Team Architects Partnership}}{Nov 2021 -- Feb 2022}
{Architectural Design Intern}{Tainan, Taiwan}
\resumeItemListStart
\resumeItem {Strategized and managed construction budget inventory.}
\resumeItem {Crafted intricate architectural models for project exhibitions.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.urbanwasabi.com.tw/}
{UrbanWasabi}}{Sep 2021 -- Nov 2021}
{Architectural Design Intern}{Tainan, Taiwan}
\resumeItemListStart
\resumeItem {Produced meticulous measured drawings for an imminent renovation project.}
\resumeItem {Spearheaded the creation of introduction videos, posters, and booklets for exhibitions.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.nckudc.com.tw/}
{NCKU Design Center}}{Jul 2021 -- Aug 2021}
{Creative Project Designer}{Tainan, Taiwan}
\resumeItemListStart
\resumeItem {Devised captivating graphic designs for NCKU's 90th-anniversary folder.}
\resumeItem {Efficiently managed the entire design-to-production workflow.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\vspace{-6pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/gamedev0003_cutthecube/}{Cut The Cube}} $|$ \emph{Unity $|$
\href{https://github.com/dadavidtseng/CutTheCube}{Git}}}{Aug 2023}
\resumeItemListStart
\resumeItem{ Engineered the 3D mesh cutting functionality.}
\resumeItem{ Established and fine-tuned the game's balance system.}
\resumeItemListEnd

\vspace{-12pt}

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/gamedev0002_trashure/}{Trashure}} $|$ \emph{Unity, Adobe Photoshop $|$ \href{https://github.com/dadavidtseng/Trashure_V3}{Git}}}{Jul 2022 -- May 2023}
\resumeItemListStart
\resumeItem{ Devised a methodology for the reinterpretation of images from field surveys.}
\resumeItem{ Pioneered the project's structure by fusing environmental themes, image media, and digital gaming.}
\resumeItemListEnd

\vspace{-12pt}

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/gamedev0001_petaverse/}{Petaverse}} $|$ \emph{Unity, Vuforia, Adobe Premiere $|$ \href{https://github.com/dadavidtseng/Petaverse}{Git}}}
{Oct 2022 -- Dec 2022}
\resumeItemListStart
\resumeItem{ Developed a commercial application model, integrating augmented reality (AR) scanning capabilities.}
\resumeItem{ Spearheaded the creation of a digital pet development system.}
\resumeItemListEnd

\vspace{-12pt}

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/architecture0003_trashcandowhat/}{Trash Can Do What}} $|$ \emph{Processing $|$ \href{https://github.com/dadavidtseng/TrashCanDoWhat}{Git}}}{Mar 2022 -- Apr 2022}
\resumeItemListStart
\resumeItem{ Compiled data from daily trash to establish a comprehensive repository.}
\resumeItem{ Visualized and crafted an interactive user interface for data exploration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Honors and Awards}
\vspace{-6pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Green Hackathon Creative Selection}}{Aug 2023}
\resumeItemListStart
\resumeItem{Best Five}
\resumeItemListEnd
\vspace{-12pt}
\resumeProjectHeading
{\textbf{9th Wuhan Golden and Silver Cup Innovation and Entreprenurship Competition}}{Aug 2023}
\resumeItemListStart
\resumeItem{Preliminary selection}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Technical Skilss-----------
\section{Skills and Languages}
\textbf{Programming Languages}{: Python, C, C\#, LaTex, SQL} \\
\textbf{Web Technologies}{: HTML, CSS, JavaScript} \\
\textbf{Software Tools}{: Unity, Blender, Rhino, Git, Adobe, Office}\\
\textbf{Languages}{: Mandarin(native), English(fluent, TOEIC 895, TOEFL 97, GRE 315), French(beginner)}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Cheng Kung University, Tainan, Taiwan}{Sep 2017 -- Jun 2023}
{Bachelor of Architecture}{GPA: 3.17/4}
%leave a line after this

\small{\textbf{Game-related Coursework: Digital Design in Creative Industries, Program Design(1), The Integration of Ar/vr for Interaction Design, Design Computation and Computational Geometry}}
\resumeSubHeadingListEnd



% adjust vscape based on the space you want to leave between each section.
\end{document}